Introduction

### 2025-11-20 Intro.Rmd
Updated plots, k-fold cross-validation, and some of the model setup

@@

```{r}
#bank_train <- 
#bank_test <- 
```

@@

#bank_glm <- glm(y ~., data = bank_train, family = binomial)
#summary(bank_glm)
```

>>>>

cat_vars <- c("job", "marital", "education", "contact", "month", "poutcome")

for (var in cat_vars) {
p <- ggplot(bank_full, aes_string(x = var, fill = "y")) +
geom_bar(position = "fill") +
coord_flip() +
labs(
title = paste("Proportion of Subscription by", var),
x = var,
y = "Proportion"
) +
theme_minimal()

print(p) 
}

@@

```{r}
#bank_train <- 
#bank_test <- 
library(caret)

kfold_cv_model <- function(data, target_col, model_func, k = 5, seed = 123, ...) {
set.seed(seed)

folds <- createFolds(data[[target_col]], k = k, list = TRUE, returnTrain = TRUE)

accuracy_list <- numeric(k)

for (i in 1:k) {
train_idx <- folds[[i]]
train_data <- data[train_idx, ]
test_data  <- data[-train_idx, ]
model <- model_func(train_data, ...)

pred_probs <- predict(model, newdata = test_data, type = "response")

if (is.numeric(pred_probs)) {
  pred <- ifelse(pred_probs > 0.5, "yes", "no")
} else {
  pred <- pred_probs
}
actual <- test_data[[target_col]]
accuracy_list[i] <- mean(pred == actual)
}
mean_accuracy <- mean(accuracy_list)
return(mean_accuracy)
}
```

@@

#bank_glm <- glm(y ~., data = bank_train, family = binomial)
#summary(bank_glm)

logistic_model <- function(train_data, ...) {
glm(y ~ ., data = train_data, family = binomial)
}

accuracy_logit <- kfold_cv_model(bank_full, "y", logistic_model, k = 5)
accuracy_logit

cat("Logistic Regression 5-Fold CV Accuracy:", round(accuracy_logit * 100, 2), "%\n")
